Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-03-27 paper.tex
update

\appendix
\section{jets parameter variations}
\textcolor{red}{KY: Please also add a section (either in the Discussion
or Appendix) to discuss about the parameter variations.
I think the figures you showed me are very important
and informative.}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}
\raggedright
\caption{Jet parameters.}
\label{tablb-jet-parameters}
\begin{tabular}{@{}llllllll@{}}
\toprule[1pt]\midrule[0.3pt]
                  & A          & B          & C          & D          & E          & F          & G          \\ \midrule
$k_{B}T$ (MeV)    & 1.720      & 17.200     & 1.720      & 0.172      & 1.720      & 1.720      & 1.720      \\
$\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\
$\beta\gamma$     & 1.2        & 0.6        & 0.6        & 0.6        & 0.6        & 0.6        & 0.3        \\ \midrule
\end{tabular}
\end{table*}

\begin{figure*}
  \includegraphics[width=\textwidth]{figures/fig__jet_parameters.png}
  \caption
   {
    Jets parameters variation around the fiducial run:\
    $\beta\gamma=1.2$ (left), $\beta\gamma=0.6$ (middle), and $\beta\gamma=0.3$ (right).
   }
  \label{fig__jet_parameters}
\end{figure*}

>>>>

\appendix
\section{jets parameter variations}

It is instructive to compare the simulation results (Fig. \ref{fig__slice-compare})\
using exactly same parameters\
except for the density ($\rho$), temperature ($k_{B}T$),\
and four-velocity ($\beta\gamma$) within the jet source.\
The parameters of jet source, including the fiducial run (C),\
covered in this appendix are given in Table \ref{tablb-jet-parameters}.

We observe that higher density (F$\rightarrow$C$\rightarrow$E) of the source\
can enhance the intensity of the shocks driven into the atmosphere,\
and makes the post-shock region hotter,\
as well as leads the bubbles to be more asymmetric about the GC.
This is because the denser jets are more likely to\
break through the thin disk in a short time\
and more difficult to be elongated by stratified atmosphere afterward.

On the other hand, when we increase the magnitude of velocity\
(G$\rightarrow$C$\rightarrow$A) such that\
the corresponding kinetic energies are the same as when increasing\
density, the bubble morphology of two will be similar.\
This demonstrates that the morphology/dynamic of bubbles is mainly determined by\
kinetic energy of a jet flow.

Finally, when we increase the thermal energy (B$\rightarrow$C$\rightarrow$D)\
of the jet source such that the thermal energy increase by\
the same amount as the kinetic energy,\
we find that the morphology of bubbles is basically unchanged,\
but the evolution of bubbles can be slightly accelerated.

\begin{table*}
\raggedright
\caption{The list of runs showing different injected jet parameters.\
         The fiducial run (C) has been pointed out by an asterisk in the list. }
\label{tablb-jet-parameters}
\begin{tabular}{@{}llllllll@{}}
\toprule[1pt]\midrule[0.3pt]
                  & A          & B          & C*         & D           & E          & F          & G          \\ \midrule
$k_{B}T$ (MeV)    & 1.720      & 0.172      & 1.720      & 17.200      & 1.720      & 1.720      & 1.720      \\
$\rho$ (g/cm$^3$) & $10^{-26}$ & $10^{-26}$ & $10^{-26}$ & $10^{-26}$  & $10^{-25}$ & $10^{-27}$ & $10^{-26}$ \\
$\beta\gamma$     & 1.40       & 0.60       & 0.60       & 0.60        & 0.60       & 0.60       & 0.28       \\ \midrule
\end{tabular}
\end{table*}

%  A    G
% 1.4 0.28

%\begin{figure*}
%  \includegraphics[width=\textwidth]{figures/fig__jet_parameters.png}
%  \caption
%   {
%    Jets parameters variation around the fiducial run:\
%    $\beta\gamma=1.2$ (left), $\beta\gamma=0.6$ (middle), and $\beta\gamma=0.3$ (right).
%   }
%  \label{fig__jet_parameters}
%\end{figure*}
